The unphysicality of Hilbert spaces

### 2023-07-12 Articles/2023-HilbertQuantum/HilbertQuantum.tex
Fixed small typo

\begin{abstract}
We show that Hilbert spaces should not be considered the ``correct'' spaces to represent quantum states mathematically. We first prove that the requirements posited by complex inner product spaces are physically justified. We then show that completeness in the infinite-dimensional case requires the inclusion of states with infinite expectations, coordinate transformations that take finite expectations to infinite ones and vice-verse, and time evolutions that transform finite expectations to infinite ones in finite time. This makes Hilbert spaces physically unsound as they model a potential infinity as an actual infinity. We argue that Schwartz spaces may be better candidates, as, among other things, guarantee that the expectation of all polynomials of position and momentum are finite, guarantee solution to the moment problem and are the only space closed under Fourier transform. We suspect that at least some problems in quantum theory related to infinities may be ultimately caused by the wrong space being used.
\end{abstract}

>>>>

\begin{abstract}
We show that Hilbert spaces should not be considered the ``correct'' spaces to represent quantum states mathematically. We first prove that the requirements posited by complex inner product spaces are physically justified. We then show that completeness in the infinite-dimensional case requires the inclusion of states with infinite expectations, coordinate transformations that take finite expectations to infinite ones and vice-versa, and time evolutions that transform finite expectations to infinite ones in finite time. This makes Hilbert spaces physically unsound as they model a potential infinity as an actual infinity. We argue that Schwartz spaces may be better candidates, as, among other things, guarantee that the expectation of all polynomials of position and momentum are finite, guarantee solution to the moment problem and are the only space closed under Fourier transform. We suspect that at least some problems in quantum theory related to infinities may be ultimately caused by the wrong space being used.
\end{abstract}
